---
title: "shiny assignment"
author: "Yangyu Chen"
output: pdf_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
library(shiny)
library(DT)  # Load the DT package

# Use iris dataset
data("iris")
iris_data <- iris

# Define the User Interface
ui <- fluidPage(
  titlePanel("Iris Dataset with DT"),
  sidebarLayout(
    sidebarPanel(
      helpText("This app displays the Iris dataset using DT for rendering tables.")
    ),
    mainPanel(
      h3("Iris Dataset"),
      DTOutput("table")  # Use DTOutput from DT package
    )
  )
)

# Define the Server Logic
server <- function(input, output, session) {
  # Render the data table
  output$table <- DT::renderDT({  # Use renderDT from DT package
    iris_data
  }, options = list(
    dom = 't',        # Suppress additional controls
    ordering = FALSE, # Disable sorting
    pageLength = 10   # Show 10 rows by default
  ))
}

# Run the Shiny App
shinyApp(ui = ui, server = server)

```
# --------------------------------------------------------------------------------
# 1. What is the difference between Hadley_1 and Hadley_2?
# --------------------------------------------------------------------------------

# Hadley_1:
# - It uses str(iris_data), which provides structural information about the dataset, 
#   including column names, types, and sample values.
# - This approach analyzes the entire dataset, making it slower for larger datasets.

# Hadley_2:
# - It uses head(iris_data, 10), which displays the first 10 rows of the dataset.
# - This approach is optimized for quick previews of the data content and is faster.

# Performance Comparison:
# - Hadley_1 is slower because it processes the entire dataset to analyze structure.
# - Hadley_2 is faster as it focuses on a subset of the data (first 10 rows).

# Conclusion:
# - Hadley_2 improves performance and is better suited for quick previews in Shiny apps.
# - Hadley_1 is more informative for initial structural analysis of datasets.

# --------------------------------------------------------------------------------
# 2. Prepare Chapters 2-4 from Mastering Shiny
# --------------------------------------------------------------------------------

# Section 2.3.5: Pairing Output Functions with Render Functions
# - renderPrint(summary(mtcars)) -> verbatimTextOutput
# - renderText("Good morning!") -> textOutput
# - renderPrint(t.test(1:5, 2:6)) -> verbatimTextOutput
# - renderText(str(lm(mpg ~ wt, data = mtcars))) -> textOutput
```{r}
# Section 3.3.6: Scatterplot of Random Numbers
ui_scatterplot <- fluidPage(
  plotOutput("plot", width = "700px", height = "300px")
)

server_scatterplot <- function(input, output, session) {
  output$plot <- renderPlot({
    plot(1:5, 
         main = "Scatterplot of Random Numbers", 
         xlab = "Index", 
         ylab = "Value", 
         col = "blue", 
         pch = 16)
  }, res = 96)
}

# Section 4.8: Render Data Table with Specific Options
library(DT) # Make sure the DT library is loaded

ui_datatable <- fluidPage(
  DTOutput("table")  # Use DTOutput instead of dataTableOutput
)

server_datatable <- function(input, output, session) {
  output$table <- renderDT({  # Use renderDT instead of renderDataTable
    iris_data
  }, options = list(
    dom = 't',       # Suppress controls
    ordering = FALSE, # Disable sorting
    pageLength = nrow(iris_data) # Display all rows
  ))
}


# Using reactable for enhanced table interactivity:
ui_reactable <- fluidPage(
  reactableOutput("table")
)

server_reactable <- function(input, output, session) {
  output$table <- renderReactable({
    reactable(
      iris_data,
      searchable = TRUE,
      sortable = TRUE,
      pagination = TRUE
    )
  })
}

# --------------------------------------------------------------------------------
# Hadley_1 Implementation
# --------------------------------------------------------------------------------

# Define the User Interface for Hadley_1
ui_hadley_1 <- fluidPage(
  titlePanel("Hadley_1: Iris Dataset Structure"),
  sidebarLayout(
    sidebarPanel(
      helpText("This app displays the structure of the Iris dataset using str().")
    ),
    mainPanel(
      h3("Structure of Iris Dataset"),
      verbatimTextOutput("structure")
    )
  )
)

# Define the Server Logic for Hadley_1
server_hadley_1 <- function(input, output, session) {
  output$structure <- renderPrint({
    time_taken <- system.time({
      structure_output <- str(iris_data)
    })
    cat("Execution Time for Structure Analysis:\n")
    print(time_taken)
    structure_output
  })
}

# --------------------------------------------------------------------------------
# Hadley_2 Implementation
# --------------------------------------------------------------------------------

# Define the User Interface for Hadley_2
ui_hadley_2 <- fluidPage(
  titlePanel("Hadley_2: Iris Dataset Preview"),
  sidebarLayout(
    sidebarPanel(
      helpText("This app displays a preview of the Iris dataset using head().")
    ),
    mainPanel(
      h3("Preview of Iris Dataset (First 10 Rows)"),
      tableOutput("preview")
    )
  )
)

# Define the Server Logic for Hadley_2
server_hadley_2 <- function(input, output, session) {
  output$preview <- renderTable({
    time_taken <- system.time({
      preview_output <- head(iris_data, 10)
    })
    cat("Execution Time for Data Preview:\n")
    print(time_taken)
    preview_output
  })
}

```


```
